SNP Analysis

### 2018-07-03 SNP_Prediction_Analysis.Rmd
Still transforming SNP

head(patient.info)

subset(sample.list, PatientID == 74)

@@

head(sample.info)
head(sample.list)

@@

ggplot(sample.info, aes(SCA.Ratio)) + geom_histogram() + facet_grid(~Status)

@@

ggplot(qcdata, aes(SCA.Ratio)) + geom_histogram() + 
  facet_wrap(~Status, scales='free_y', ncol=1) + labs(x='SCA Ratio', title='SCA Ratio, normal vs BE')

ggplot(subset(qcdata, SampleType == 'BE'), aes(Purity, SCA.Ratio, color=Status)) + geom_point() + 
  geom_vline(xintercept = 0.95, color='red') + geom_hline(yintercept = 0.05, color='red')

ggplot(subset(qcdata, SampleType == 'BE'), aes(Ploidy, SCA.Ratio, color=Status)) + geom_point() + 
  geom_hline(yintercept = 0.05, color='red')
```

```{r}
## 43% of P samples have low/no CN with a ploidy of 2 or less
nrow(subset(qcdata, Status == 'P' & SampleType == 'BE' & SCA.Ratio <= 0.05 & Ploidy <= 2))/nrow(subset(qcdata, Status == 'P' & SampleType == 'BE'))

## <1% of P samples have no apparent CN
nrow(subset(qcdata, Status == 'P' & SCA.Ratio <= 0 & SampleType == 'BE'))/nrow(subset(qcdata, Status == 'P' & SampleType == 'BE'))

## 36% of P samples have < 5% CN and high purity ()
nrow(subset(qcdata, Status == 'P' &  Purity >= 0.95 & SCA.Ratio <= 0.05 & SampleType == 'BE'))/nrow(subset(qcdata, Status == 'P' & SampleType == 'BE'))

@@

# For those patients with low SCA samples, a large proportion of them show low SCA in most/all of their samples
hist(round(lowscaSamples/totalSamples[names(lowscaSamples)], 2))

@@

```{r, warning=F}
mergedSegs = NULL
mergedArms = NULL
length(ptdirs)

for (pt in ptdirs) {
  if (length(list.files(pt, '*wins_tiled.txt', full.names=T)) <= 0) {
    message(paste("No tiled files for",pt))
    next
  }

@@

@@

```{r normals, fig.width=6, fig.height=8}
rownames(mergedSegs) = sub('\\.LogR','',rownames(mergedSegs))
nm = melt(mergedSegs[grep('BLD|gastric', rownames(mergedSegs), ignore.case=T),])
be = melt(mergedSegs[grep('BLD|gastric', rownames(mergedSegs), ignore.case=T, invert=T),])
```

@@

```{r rnormals, echo=F, fig.width=8, fig.height=8}
randNormal = sample(grep('BLD|gastric', rownames(mergedSegs), ignore.case=T, value=T), 1)
pt = unlist(strsplit(randNormal, '_'))[1]
segments.list[[pt]] = subset(segments.list[[pt]], chr %in% c(1:22))
segments.list[[pt]]$chr = factor(segments.list[[pt]]$chr, levels=c(1:22), ordered = T)

grid.arrange(
  ggplot(subset(segments.list[[pt]], sample == paste(randNormal,'.LogR',sep='')), aes(y=medLRR)) + 
    facet_grid(~chr, scales='free_x',space='free_x') +
    geom_segment(aes(x=startpos, xend=endpos, y=medLRR, yend=medLRR), size=2) + ylim(-1,1) +
    theme(axis.text.x=element_blank(), panel.spacing.x=unit(0, 'lines')) +
    labs(title='Median LRR, ASCAT segments', subtitle=pt), 
  ggplot(subset(nm, Var1 == randNormal), aes(Var2, value)) + geom_point() + ylim(-1,1) + 
    theme(axis.text.x=element_blank()) + labs(title='Winsorized LRR, binned'),  
top='Random BLD or gastric normal', bottom=randNormal)

@@

grid.arrange(
  ggplot(subset(segments.list[[pt]], sample == randBE), aes(y=medLRR)) + 
    facet_grid(~chr, scales='free_x',space='free_x') +
    geom_segment(aes(x=startpos, xend=endpos, y=medLRR, yend=medLRR), size=2) + ylim(1,-1) +
    theme(axis.text.x=element_blank(), panel.spacing.x=unit(0, 'lines')) +
    labs(title='Median LRR, ASCAT segments', subtitle=pt), 
  ggplot(subset(be, Var1 == sub('\\.LogR','',randBE)), aes(Var2, value)) + geom_point() + ylim(-1,1) + 
    theme(axis.text.x=element_blank()) + labs(title='Winsorized LRR, binned'),  
top='BE', bottom=randBE)

@@

I adjust the variance of each genomic region by the mean and sd extracted when I trained on the sWGS data. This seems to be a more fair comparison than scaling all the new data to itself, but the predictions don't really change.
```{r, warning=F}
# uv 
# ms  = t(apply(mergedSegs, 1, function(sample) {
#   sapply(1:ncol(mergedSegs), function(i){
#     unit.var(sample[i], z.mean[i], z.sd[i])
#   })
# }))
# 
# range(ms)
ms = mergedSegs
for (i in 1:ncol(ms)) {
  ms[,i] = unit.var(ms[,i])
  #ms[,i] = unit.var(ms[,i], z.mean[i], z.sd[i])
}
range(ms)
dim(ms)
# ma  = t(apply(mergedArms, 1, function(sample) {
#   sapply(1:ncol(mergedArms), function(i){
#     unit.var(sample[i], z.arms.mean[i], z.arms.sd[i])
#   })
# }))

ma = mergedArms
for (i in 1:ncol(ma)) {
  ma[,i] = unit.var(ma[,i])
}
range(ma)
dim(ma)

nm = melt(ms[grep('BLD|gastric', rownames(ms), ignore.case=T),])
be = melt(ms[grep('BLD|gastric', rownames(ms), ignore.case=T, invert=T),])
```

The variance gets much bigger after unit normalizing, but the difference between BE and normal is still clear.

@@

@@

preds = preds %>% dplyr::mutate( 
  'Adj. RR'=RR+offset,  
  'Adj. Prob'=1/(1+exp(-RR+abs(offset)) )
)

@@

```{r}
hist(subset(preds, Samplename %in% lowsca$Samplename)$Prob)

@@

be = subset(preds, !grepl('BLD|gastric', Samplename, ignore.case=T))
grid.arrange(
  ggplot(be, aes(Prob)) + geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
    scale_fill_gradientn(colors = myPal,  name='') + 
    labs(title='Predictions on BE', y='n Samples', x='Unadjusted Probability'),
top='BE samples' )

So how do these high normals look?
```{r}
preds
qcdata
nrow(preds)

pred.qc = base::merge(preds, qcdata, by='Samplename')

@@

Compare BLD to BE
```{r, echo=F, fig.height=8}
bld = preds[grep('BLD', preds$Samplename, ignore.case=T),]
grid.arrange(
  ggplot(bld, aes(Prob)) + geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(y='n Samples', x='Unadjusted Probability'),
ggplot(bld, aes(`Adj. Prob`)) + geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(y='n Samples', x='Adjusted Probability'), top='Predictions on BLD samples only' )

length(which(bld$Prob < 0.5))/nrow(bld)
length(which(bld$`Adj. Prob` < 0.5))/nrow(bld)

be = preds[grep('BLD|gastric', rownames(preds), ignore.case=T, invert = T),]
grid.arrange(
  ggplot(be, aes(Prob)) + geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
    scale_fill_gradientn(colors = myPal,  name='') + 
    labs(y='n Samples', x='Unadjusted Probability'),
  ggplot(be, aes(`Adj. Prob`)) + geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
    scale_fill_gradientn(colors = myPal,  name='') + 
    labs(y='n Samples', x='Adjusted Probability'), top='Predictions on BE only'
)

unadj = length(unique(sapply(rownames(be[which(be$Prob > 0.5),]), function(x) unlist(strsplit(x, '_'))[1])))/length(patients)
adj = length(unique(sapply(rownames(be[which(be$`Adj. Prob` > 0.5),]), function(x) unlist(strsplit(x, '_'))[1])))/length(patients)

Unajdusted `r round(unadj,2)*100`% of BE patients have a >50% probability of progression.  Adjusted, `r round(adj, 2)*100`% have a >50% probability.

@@

```{r}

#preds.info = base::merge(sample.info, preds, by='Samplename')

rows = grep('BLD|gastric', pred.qc$Samplename, ignore.case=T)
normals = pred.qc[rows,]
pred.qc = pred.qc[-rows,]
nrow(pred.qc)

@@

rocNoLow = pROC::roc(Status ~ Prob, data=subset(pred.qc, !Samplename %in% lowsca$Samplename), auc=T, ci=T, of='thresholds')
roc.plot(rocNoLow)

@@

roct1 = pROC::roc(Status ~ Prob, data=subset(pred.qc, Timepoint == 'T1'), auc=T, ci=T, of='thresholds')
roc.plot(roct1)

roct2 = pROC::roc(Status ~ Prob, data=subset(pred.qc, Timepoint != 'T1'), auc=T, ci=T, of='thresholds')
roc.plot(roct2)

qcpred = subset(pred.qc, Samplename %in% subset(qcdata, Purity > 0.8 & Goodnessoffit >= 0.9)$Samplename)
qc = pROC::roc(Status ~ Prob, data=qcpred, auc=T, ci=T, of='thresholds')
roc.plot(qc)

@@

## Regression using SNP Data

```{r, echo=F, eval=F}

sample.info = patient.info[c('PatientID','Status')]
sample.info = base::merge(sampleInfo, sample.info, by='PatientID', all.x=T)

sample.info = subset(sample.info, !Level %in% c('BLD','GASTRIC'))
sample.info$Samplename = with(sample.info, paste(PatientID, SampleID, EndoscopyID, Level, sep='_'))

df = arrayDf
arrayDf = arrayDf[grep('BLD|GASTRIC',rownames(df), invert=T),]
rownames(arrayDf) = sub('\\.LogR','',rownames(arrayDf))

patient.info
status = vector(length=nrow(arrayDf), mode='character')
names(status) = rownames(arrayDf)

for (i in 1:length(status))
  status[i] = unique(subset(patient.info, PatientID == sub('_.*','',names(status)[i]))[,'Status'])

labels = as.integer(factor(labels))-1
names(labels) = names(status)
rm(status)

@@

nl = 1000;folds = 10; splits = 5 
sets = create.patient.sets(sample.info[c('PatientID','Samplename','Status')], folds, splits, 0.2)

alpha.values = c(0,0.5,0.9,1)
## ----- All ----- ##
coefs = list(); plots = list(); performance.at.1se = list(); models = list(); cvs = list()
cache.dir = '~/Data/Ellie/Analysis/SNP/'
dir.create(cache.dir, recursive = T, showWarnings = F)
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
if (file.exists(file)) {
  message(paste("loading", file))
  load(file, verbose=T)
} else {
  for (a in alpha.values) {
    fit0 <- glmnet(arrayDf, labels, alpha=a, nlambda=nl, family='binomial', standardize=F)    
    l = fit0$lambda

    cv.patient = crossvalidate.by.patient(x=arrayDf, y=labels, lambda=l, pts=sets, a=a, nfolds=folds, splits=splits, fit=fit0, select='deviance', opt=-1, standardize=F)

>>>>

@@

@@

@@

ggplot(qcdata, aes(SCA.Ratio)) + geom_histogram() + 
  facet_wrap(~Status, scales='free_y', ncol=1) + labs(x='SCA Ratio', title='SCA Ratio, NP vs P')

ggplot(subset(qcdata, SampleType == 'BE'), aes(Purity, SCA.Ratio, color=Status)) + geom_point() + 
  geom_vline(xintercept = 0.95, color='red') + geom_hline(yintercept = 0.05, color='red') + 
  labs(title='Barretts only')

ggplot(subset(qcdata, SampleType == 'BE'), aes(Ploidy, SCA.Ratio, color=Status)) + geom_point() + 
  geom_hline(yintercept = 0.05, color='red') + labs(title='Barretts only')

## Low CN
lowPloidyCN = subset(qcdata, Status == 'P' & SampleType == 'BE' & SCA.Ratio <= 0.05 & Ploidy <= 2)

## samples have no apparent CN
noCN = subset(qcdata, Status == 'P' & SCA.Ratio <= 0 & SampleType == 'BE')

## high CN | ploidy, nonP
highPloidyCN = subset(qcdata, Status == 'NP' & SampleType == 'BE' & (SCA.Ratio >= mean(qcdata$SCA.Ratio,na.rm=T)+ sd(qcdata$SCA.Ratio,na.rm=T)*2 | Ploidy >= 2.3))

#### P: Low SCA, Ploidy<=2
`r round(nrow(lowPloidyCN)/nrow(subset(qcdata, Status == 'P' & SampleType == 'BE')), 3)*100`% of PROGRESSOR samples have <5% SCA and an ASCAT ploidy of 2 or less. Most of these show a >90% purity as well.
`r pander(summary(lowPloidyCN$Purity))`

#### P: No SCA
`r round(nrow(noCN)/nrow(subset(qcdata, Status == 'P' & SampleType == 'BE')), 3)*100`% of PROGRESSOR samples have 0 SCA

#### NP: High CN or ploidy > 2.3
`r round(nrow(highPloidyCN)/nrow(subset(qcdata, Status == 'NP' & SampleType == 'BE')), 3)*100`% of NON-PROGRESSOR samples have >2SD SCA (~25%) or high ploidy.

```{r, echo=F}

@@

# For those patients with low SCA samples, a large proportion of them show low SCA in most/all of their samples
#plot(round(lowscaSamples/totalSamples[names(lowscaSamples)], 2))

pt = sub('_.*', '', lowPloidyCN$Samplename[1])
pfiles = list.files(paste('/Volumes/fh/fast/reid_b/collab/Killcoyne/Data/PerPatient', pt, sep='/'), full.names = T)
load(grep('ascat.Rdata', pfiles, value=T), verbose=T)
head(ascat.output$segments_raw)
seg = subset(ascat.output$segments_raw, grepl(lowPloidyCN$Samplename[1], sample))
seg$chr = factor(seg$chr, levels=c(1:22,'X','Y'))

plot.seg<-function(seg, incAB=F) {
  p = ggplot(seg) + facet_grid(~chr, space='free_x', scales='free_x') + 
    geom_segment(aes(x=startpos, xend=endpos, y=medLRR, yend=medLRR), color='darkgreen', size=3)

  if (incAB)
    p = p + geom_segment(aes(x=startpos, xend=endpos, y=nAraw+nBraw, yend=nAraw+nBraw), color='blue', size=3)

  p + theme(axis.text.x=element_blank() )
}

plot.seg(seg,incAB = T) + labs(title=paste('Low SCA Prog sample',lowPloidyCN$Samplename[1]), x='')

pt = sub('_.*', '', highPloidyCN$Samplename[1])
pfiles = list.files(paste('/Volumes/fh/fast/reid_b/collab/Killcoyne/Data/PerPatient', pt, sep='/'), full.names = T)
load(grep('ascat.Rdata', pfiles, value=T), verbose=T)
head(ascat.output$segments_raw)
seg = subset(ascat.output$segments_raw, grepl(highPloidyCN$Samplename[1], sample))
seg$chr = factor(seg$chr, levels=c(1:22,'X','Y'))

plot.seg(seg, incAB = T) + labs(title=paste('High SCA Non-Prog sample',highPloidyCN$Samplename[1]), x='')

@@

```{r, warning=F}

if (file.exists('tmp_seg_pt.Rdata')) {
  load('tmp_seg_pt.Rdata', verbose=T) 
} else {

mergedSegs = NULL
mergedArms = NULL
length(ptdirs)

for (pt in ptdirs) {
  print(pt)
  if (length(list.files(pt, '*wins_tiled.txt', full.names=T)) <= 0) {
    message(paste("No tiled files for",pt))
    next
  }

@@

save(mergedSegs, mergedArms, file='tmp_seg_pt.Rdata')
}

rownames(mergedSegs) = sub('\\.LogR','', rownames(mergedSegs))
rownames(mergedArms) = sub('\\.LogR','', rownames(mergedArms))

@@

```{r normals, fig.width=6, fig.height=8, eval=F}
nm = melt(mergedSegs[grep('BLD|gastric', rownames(mergedSegs), ignore.case=T),])
be = melt(mergedSegs[grep('BLD|gastric', rownames(mergedSegs), ignore.case=T, invert=T),])

grid.arrange(
  ggplot(nm, aes(Var2, value, group=Var2)) + geom_point() + labs(title='Blood/gastric') + theme(axis.text.x = element_blank()),
  ggplot(be, aes(Var2, value, group=Var2)) + geom_point() + labs(title='BE samples') + theme(axis.text.x = element_blank())
)

@@

```{r rnormals, echo=F, fig.width=8, fig.height=8, eval=F}
randNormal = sample(grep('BLD', rownames(mergedSegs), ignore.case=T, value=T), 1)
pt = unlist(strsplit(randNormal, '_'))[1]
segments.list[[pt]] = subset(segments.list[[pt]], chr %in% c(1:22))
segments.list[[pt]]$chr = factor(segments.list[[pt]]$chr, levels=c(1:22), ordered = T)

grid.arrange(
  plot.seg(subset(segments.list[[pt]], sample == paste(randNormal,'.LogR',sep=''))) + labs(title='Median LRR, ASCAT segments', x='', subtitle=pt),
  ggplot(melt(as.matrix(mergedSegs[randNormal,])), aes(Var1, value)) + geom_point() + labs(title='Winsorized') + ylim(-1,1) + theme(axis.text.x=element_blank()),
top='Random BLD or gastric normal', bottom=randNormal)

@@

grid.arrange(
  plot.seg(subset(segments.list[[pt]], sample == randBE)) +
    labs(title='Median LRR, ASCAT segments', subtitle=pt), 
  ggplot(melt(as.matrix(mergedSegs[sub('\\.LogR','',randBE),])), aes(Var1, value)) + geom_point() + ylim(-1,1) + 
    theme(axis.text.x=element_blank()) + labs(title='Winsorized LRR, binned'),  
top='BE', bottom=randBE)

@@

I adjust the variance of each genomic region by the mean and sd extracted when I trained on the sWGS data. This seems to be a more fair comparison than scaling all the new data to itself, but the predictions don't really change.
```{r, warning=F}
# uv 
# ms  = t(apply(mergedSegs, 1, function(sample) {
#   sapply(1:ncol(mergedSegs), function(i){
#     unit.var(sample[i], z.mean[i], z.sd[i])
#   })
# }))
# 
# range(ms)
ms = mergedSegs
for (i in 1:ncol(ms)) {
  #ms[,i] = unit.var(ms[,i])
  ms[,i] = unit.var(ms[,i], z.mean[i], z.sd[i])
}
range(ms)
dim(ms)
# ma  = t(apply(mergedArms, 1, function(sample) {
#   sapply(1:ncol(mergedArms), function(i){
#     unit.var(sample[i], z.arms.mean[i], z.arms.sd[i])
#   })
# }))

ma = mergedArms
for (i in 1:ncol(ma)) {
  #ma[,i] = unit.var(ma[,i])
  ma[,i] = unit.var(ma[,i], z.arms.mean[i], z.arms.sd[i])
}
range(ma)
dim(ma)

nm = melt(ms[grep('BLD|gastric', rownames(ms), ignore.case=T),])
be = melt(ms[grep('BLD|gastric', rownames(ms), ignore.case=T, invert=T),])

grid.arrange(
  ggplot(be, aes(Var2, value, group=Var2)) + geom_point() + labs(title='BE samples'),
  ggplot(nm, aes(Var2, value, group=Var2)) + geom_point() + labs(titls='Blood/gastric')
)

@@

ggplot(melt(arrayDf), aes(Var2, value, group=Var2)) + geom_point() + labs(title='All, scaled')

@@

# preds = preds %>% dplyr::mutate( 
#   'Adj. RR'=RR+offset,  
#   'Adj. Prob'=1/(1+exp(-RR+abs(offset)) )
# )

@@

```{r, eval=F}
hist(subset(preds, Samplename %in% lowsca$Samplename)$Prob)

@@

be = subset(preds, !grepl('BLD|gastric', Samplename, ignore.case=T))
grid.arrange(
  ggplot(be, aes(Prob)) + geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
    scale_fill_gradientn(colors = myPal,  name='') + 
    labs(title='Predictions on BE', y='n Samples', x='Unadjusted Probability'),
top='BE samples' )
pred.qc = base::merge(preds, qcdata, by='Samplename')
```

So how do these high normals look?
```{r, eval=F}
preds
qcdata
nrow(preds)

@@

Compare BLD to BE
```{r, echo=F, fig.height=8}

unadj = length(unique(sapply(rownames(be[which(be$Prob > 0.5),]), function(x) unlist(strsplit(x, '_'))[1])))/length(patients)
#adj = length(unique(sapply(rownames(be[which(be$`Adj. Prob` > 0.5),]), function(x) unlist(strsplit(x, '_'))[1])))/length(patients)
#Adjusted, `r round(adj, 2)*100`% have a >50% probability.
```

Unajdusted `r round(unadj,2)*100`% of BE patients have a >50% probability of progression.

@@

```{r roc, echo=T}
#preds.info = base::merge(sample.info, preds, by='Samplename')
rows = grep('BLD|gastric', pred.qc$Samplename, ignore.case=T)
normals = pred.qc[rows,]
pred.qc = pred.qc[-rows,]
nrow(pred.qc)

@@

rocNoLow = pROC::roc(Status ~ Prob, data=subset(pred.qc, !Samplename %in% c(lowsca$Samplename,highPloidyCN$Samplename)), auc=T, ci=T, of='thresholds')
roc.plot(rocNoLow)

@@

per_pt_ex = subset(pred.qc, !Samplename %in% c(lowsca$Samplename,highPloidyCN$Samplename)) %>% group_by(PatientID, Timepoint, Status) %>% dplyr::summarise(
  max.Prob = max(Prob), max.RR = max(RR)
)

rocppex = pROC::roc(Status ~ max.Prob, data=per_pt_ex, auc=T, ci=T, of='thresholds')
roc.plot(rocppex)

roct2 = pROC::roc(Status ~ Prob, data=subset(pred.qc, Timepoint != 'T1' & !Samplename %in% c(lowsca$Samplename,highPloidyCN$Samplename)), auc=T, ci=T, of='thresholds')
roc.plot(roct2)

@@

# Regions predicted by model
Not evaluated currently
```{r coefs, eval=F}
features = coefs$`0.9`[,1,drop=F]

locs = do.call(rbind.data.frame, c(strsplit(rownames(features), ':|-'), stringsAsFactors=F))
colnames(locs) = c('chr','start','end')
locs[] = lapply(locs[], as.numeric)

feature.locs = makeGRangesFromDataFrame(locs)

gr = makeGRangesFromDataFrame(segments.list$`512`, start.field = 'startpos', end.field = 'endpos', keep.extra.columns = T)

ov = findOverlaps(feature.locs, gr)

feature.locs[unique(queryHits(ov))]

cna = lapply( unique(queryHits(ov)), function(hit) {
  tmp = gr[subjectHits(ov[queryHits(ov) == hit])]
  tmp = subset(as.data.frame(tmp), nMajor+nMinor > 2.3 | nMajor+nMinor < 1.5) %>% group_by(sample, nMajor+nMinor) %>% dplyr::summarise( n=length(sample), medLRR=mean(medLRR), mn.bp=mean(end-start) ) %>% rowwise() %>% 
    dplyr::mutate( type=ifelse(`nMajor + nMinor` >= 3, 1, 0))
})
names(cna) = rownames(features)

fl = sapply(cna, function(x) length(unique(x$sample)))
feature.locs[which(fl == 0)]

cna.count = do.call(rbind, lapply(cna, function(x) table(x$type)))

cna.mx = as.matrix(sapply(cna, function(x) length(unique(x$sample))))
cna.mx = cbind('sample.cnt'=cna.mx, 'loss'=NA,'gain'=NA, 'loss.bp', 'gain.bp')
for (ft in rownames(features)) {
  cna.mx[ft,c('loss','gain')] = c(0,0)
  if (nrow(cna[[ft]]) > 0)
    cna.mx[ft,c('loss','gain')] = c(length(which(cna[[ft]]$type == 0)),length(which(cna[[ft]]$type == 1)))

  median(cna[[ft]] [[cna[[ft]]$type == 0,'mn.bp']] )

}

cna$`1:59820150-64805161`

# Regression using SNP Data

```{r regression, echo=F, eval=F}
slabels = sample.info[,c('PatientID','Status', 'Samplename')]

missing = setdiff(sample.info$Samplename, rownames(arrayDf))
rows = grep('BLD|gastric', rownames(arrayDf), ignore.case=T)
bld_gastric = arrayDf[rows,]

df = arrayDf[-rows,]

slabels = subset(slabels, Samplename %in% rownames(df))

status = as.integer(as.factor(slabels$Status))-1
names(status) = slabels$Samplename

df = df[-grep(setdiff(rownames(df),names(status)), rownames(df)),]

#df = arrayDf[which(!rownames(arrayDf) %in% c(lowsca$Samplename,highPloidyCN$Samplename)),]

@@

nl = 1000;folds = 10; splits = 5 
sets = create.patient.sets(slabels, folds, splits, 0.2)

#sets = create.patient.sets(subset(sample.info, !Samplename %in% c(lowsca$Samplename,highPloidyCN$Samplename)) [c('PatientID','Samplename','Status')], folds, splits, 0.2)

alpha.values = c(0,0.5,0.9,1)
## ----- All ----- ##
coefs = list(); plots = list(); performance.at.1se = list(); models = list(); cvs = list()
cache.dir = '~/Data/Ellie/Analysis/SNP/'
dir.create(cache.dir, recursive = T, showWarnings = F)
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
#if (file.exists(file)) {
#  message(paste("loading", file))
#  load(file, verbose=T)
#} else 
  {
  for (a in alpha.values) {
    fit0 <- glmnet(df, status, alpha=a, nlambda=nl, family='binomial', standardize=F)    
    autoplot(fit) + theme(legend.position="none")
    l = fit0$lambda

    cv.patient = crossvalidate.by.patient(x=df, y=status, lambda=l, pts=sets, a=a, nfolds=folds, splits=splits, fit=fit0, select='deviance', opt=-1, standardize=F)
